\documentclass[sigconf, authordraft, anonymous]{acmart}

\input{./tex/preamble.tex}

\setcopyright{rightsretained}

% DOI
\acmDOI{10.1145/nnnnnnn.nnnnnnn}

% ISBN
\acmISBN{978-x-xxxx-xxxx-x/YY/MM}

% Conference
\acmConference[GECCO '18]{the Genetic and Evolutionary Computation
Conference 2018}{July 15--19, 2018}{Kyoto, Japan}
\acmYear{2018}
\copyrightyear{2018}

\acmPrice{15.00}

\acmSubmissionID{123-A12-B3}

\begin{document}

\title{Humane approach to Starcraft micromanagement}

\author{Benoît Cortier}
\affiliation{\institution{University of Technology of Belfort-Montbéliard}
             \streetaddress{90010 cedex}
             \city{Belfort}
             \country{France}
             }
\affiliation{\institution{University of Tsukuba, Graduate School of Systems and Information Engineering}
             \streetaddress{Tennodai 1-1-1}
             \city{Tsukuba City}
             \country{Japan}
             }
\email{benoit.cortier@fried-world.eu}

\author{Claus Aranha}
\affiliation{\institution{University of Tsukuba, Faculty of Engineering, Information and Systems}
             \streetaddress{Tennodai 1-1-1}
             \city{Tsukuba City}
             \country{Japan}
             }
\email{caranha@cs.tsukuba.ac.jp}

% 174 words (Maximum 200 words)
\begin{abstract}
We study the use of NEAT and variants to develop strategies for the
micromanagement of squads of units in the Starcraft: Brood Wars game.
While current research in this field focuses on developing strategies
that maximize win rate, we are interested in also minimizing the amount
of losses in terms of destroyed units. This is important when one considers
that Starcraft battles are in the context of a longer strategic play session,
and in this sense conserving resources is important. To achieve this goal,
we defined a fitness function that takes into account the number of
surviving units, and experimented with four NEAT variants: vanilla NEAT,
novelty-search NEAT, unified (or homogeneous) NEAT and cascade NEAT. We
explored these four variants on with four different units match ups. The
four variants performed similarly on win ratio and survival metrics.
However, we performed a qualitative analysis as well and found that differents
behaviours emerged or that they emerged in different ways. From all that we draw
ideas for future work that could achieve our original goal.
\end{abstract}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010405.10010476.10011187.10011190</concept_id>
<concept_desc>Applied computing~Computer games</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Applied computing~Computer games}

\keywords{Starcraft, micromanagement, NEAT, neuroevolution, artificial
          neural networks, evolutionary algorithms, RTS}

\maketitle

\input{./tex/introduction}

\input{./tex/background}

\input{./tex/proposal}

\input{./tex/matchups-experiments}

\input{./tex/experiments-results}

\input{./tex/discussion}

\input{./tex/conclusion}

\section*{Acknowledgements}

AUTHOR 1 was partially funded by ACKNOWLEDGEMENT 1.

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}{}

\end{document}

