\section{Experiments and results}\label{section:experiments-results}

\subsection{Qualitative results (behaviours)}

\subsubsection{Developping stimpack behaviour}

Vanilla NEAT doesn’t seems to be good a developing the stimpack behaviour since organisms
that survives without stimpack get better reward,
even though they may have survived because others used stimpacks to get in the frontline
and got themselves killed first.
So, organisms tends to lose this behaviour over generations.

CHECK: Cascade-NEAT and Novelty [expected to be approximately identical].

In comparison, the unified version, which is good a developing uniform behaviours
was somewhat better at developing this behaviour.
Indeed, since every agents use the same type of neural network, all units in the round
has the behaviour encoded and don’t win because others
did all the hard stuff.

Sadly the marines vs marines problem can be solved efficiently just by waiting for the
enemy and attacking all out mostly without stimpacks.
Depending on the enemy’s formation at it’s arrival it can be even more effective.
They can indeed shoot first with more firepower.

Novelty search got a significantly better result on the marines vs zergs experiments,
meaning it was able to develop some stimpack behaviours. [need more behaviour analysis]

Conclusion: not a big success. Overall failure.

\subsubsection{Kiting behaviour}

…


\subsubsection{Others}

…

\subsection{Quantitative results (statistical)}

\subsubsection{Survivors and victory comparison}

…

